R MINOS Lineplot Notebooks

### 2023-06-15 minos/outcomes/make_lineplots_all.Rmd
fix child uplift directories

IMPORTANT NOTE TO RUN PYTHON YOU NEED TO SET THE PYTHON INTERPRETER 
IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS.

@@

```{r setup, include=FALSE}
library(reticulate) # for python in Rmd. 
library(knitr)
require(here)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
knitr::knit_engines$set(python = reticulate::eng_python)
reticulate::use_condaenv("minos_conda", required = TRUE)
```

@@

```{python all_child_uplift_SF_12, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,hhIncomeIntervention"
tags = "Baseline,All Child Uplift"
subset_function_strings = "who_kids,who_boosted"
prefix="baseline_all_child_uplift"
config_mode = "default_config"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
```

@@

```{python all_five_SF_12, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,hhIncomeIntervention,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
tags = "Baseline,All Child Uplift,Poverty Line Child Uplift,Living Wage Intervention,Energy Downlift"
subset_function_strings = "who_alive,who_boosted,who_boosted,who_boosted,who_boosted"
prefix="all_five_combined"
config_mode = "default_config"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
```

>>>>

IMPORTANT NOTE TO RUN PYTHON YOU NEED TO SET THE PYTHON INTERPRETER 
IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS. 
NOT SURE THIS IS NEEDED ANYMORE GIVEN WE'RE SETTING THE CONDA ENV MANUALLY.

@@

```{r setup, include=FALSE}
require(reticulate) # for python in Rmd. 
require(knitr)
require(here)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
knitr::knit_engines$set(python = reticulate::eng_python)
reticulate::use_condaenv("minos_conda", required = FALSE)
```

@@

```{python all_child_uplift_SF_12, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,hhIncomeChildUplift"
tags = "Baseline,All Child Uplift"
subset_function_strings = "who_kids,who_boosted"
prefix="baseline_all_child_uplift"
config_mode = "default_config"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
```

@@

```{python all_five_SF_12, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,hhIncomeChildUplift,hhIncomePovertyLineChildUplift,livingWageIntervention,energyDownlift"
tags = "Baseline,All Child Uplift,Poverty Line Child Uplift,Living Wage Intervention,Energy Downlift"
subset_function_strings = "who_alive,who_boosted,who_boosted,who_boosted,who_boosted"
prefix="all_five_combined"
config_mode = "default_config"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="Baseline", v="SF_12", method='nanmean')
```
